Title Goes Here

### 2023-11-02 paper/main.tex
add initial graphs

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algorithmic}  %% typset algorithms
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}

@@

% use quotes as smart-quotes. https://tex.stackexchange.com/a/52354
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

@@

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm,algorithmic}  %% typset algorithms

\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}

@@

% use quotes as smart-quotes. https://tex.stackexchange.com/a/52354
%\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\usepackage{graphicx}

@@

\appendices

\section{Additional Experimental Results}

% figures for the main body
\begin{figure*}
  \centering
  \newcommand{\gsize}{.45\textwidth}
\begin{tabular}{c| c c}
    \hline\hline
  & \textbf{OT-Based (GMW)} & \textbf{Beaver Triple-Based}\\
    \hline\hline
  \rotatebox{90}{\phantom{hellohello}$n$-bit addition}
  & \includegraphics[width=\gsize]{graphs/security_adder_gmw_128_1024.pdf}
                 & \includegraphics[width=\gsize]{graphs/security_adder_beaver_128_1024.pdf} \\
    \hline
  \rotatebox{90}{\phantom{hel}$n$-bit less-than comparison}
  & \includegraphics[width=\gsize]{graphs/security_less_than_gmw_128_1024.pdf}
                 & \includegraphics[width=\gsize]{graphs/security_less_than_beaver_128_1024.pdf} \\
    \hline
  \rotatebox{90}{\phantom{h}$n$-bit Beaver triple generation}
  & \includegraphics[width=\gsize]{graphs/security_beaver_triple_gen_gmw_128_1024.pdf}
                 & \includegraphics[width=\gsize]{graphs/security_beaver_triple_gen_beaver_128_1024.pdf} \\
    \hline
    \hline
\end{tabular}
\caption{Experimental results.}
\end{figure*}

\begin{figure*}
  \centering
  \newcommand{\gsize}{.45\textwidth}
\begin{tabular}{c| c c}
    \hline\hline
  & \textbf{OT-Based (GMW)} & \textbf{Beaver Triple-Based}\\
    \hline\hline
  \rotatebox{90}{\phantom{hellohello}$n$-bit addition}
  & \includegraphics[width=\gsize]{graphs/time_adder_gmw_256_2048.pdf}
                 & \includegraphics[width=\gsize]{graphs/time_adder_beaver_256_2048.pdf} \\
    \hline
  \rotatebox{90}{\phantom{hel}$n$-bit less-than comparison}
  & \includegraphics[width=\gsize]{graphs/time_less_than_gmw_256_2048.pdf}
                 & \includegraphics[width=\gsize]{graphs/time_less_than_beaver_256_2048.pdf} \\
    \hline
  \rotatebox{90}{\phantom{h}$n$-bit Beaver triple generation}
  & \includegraphics[width=\gsize]{graphs/time_beaver_triple_gen_gmw_256_2048.pdf}
                 & \includegraphics[width=\gsize]{graphs/time_beaver_triple_gen_beaver_256_2048.pdf} \\
    \hline
    \hline
\end{tabular}
\caption{Experimental results: decision tree training time.}
\end{figure*}

\input{full_figures.tex}
